DOpElib: Differential Equations and Optimization Environment; A Goal Oriented Software Library for Solving PDEs and Optimization Problems

### 2012-11-08 Paper_May_2012/main.tex
Templates und Code angeglichen, trotzdem noch unterschiede im coding-style, allerdings wird der Code von vorne nach hinten immer sparsamer, was ja durchaus zu begruenden ist. Eventuell vorne noch mehr kuerzen?

Finally, we note that to compute the requested functional value 
all that is left is to evaluate the functional in the computed solution 
which can be done again using an appropriate integrator method.
Since the sequence of events sketched above is again independent of the 
exact problem we introduce another container around it which we call 
\texttt{StatPDEProblem} that then simply provides the user with the 
method
\begin{lstlisting}
      void StatPDEProblem::ComputeReducedFunctionals();
\end{lstlisting}
That combines all the necessary steps to calculate $J(u_h)$.

@@

  LocalPDE<VECTOR> local_pde;
  LocalFunctional<VECTOR> local_functional;

@@

  SpaceTimeHandler<TRIANGULATION, FE> dof_handler(triangulation,
                                                  finite_element);

@@

  PDEProblemContainer<LocalPDE> prob_container(local_pde,
                                               dof_handler);
\end{lstlisting}
After that, we add the functional under consideration and, because it is a boundary functional, we specify the part of the boundary on which the functional operates (this is done via a 'boundary color', $1$ represents $\Gamma_{circ}$).
\begin{lstlisting}

@@

  typedef StatPDEProblem<NEWTONSOLVER,
           PDEProblemContainer<LocalPDE>, VECTOR, 2> SSOLVER;

@@

  typedef NewtonSolver<LINEARSOLVER, VECTOR, 2> NEWTONSOLVER;

\end{lstlisting}
The first template parameter of \texttt{NewtonSolver} describes which linear solver we use in this example. We opted for a direct solver, so: 
\begin{lstlisting}

  typedef DirectLinearSolverWithMatrix<MATRIX,
            VECTOR, 2> LINEARSOLVER;

@@

The pressure and incompressibility terms should be 
treated fully implicitly when time-discretizing 
the Navier-Stokes equations.
For this reason, the implementation is split up
into several items to account for fully implicit 
terms and remaining terms for which we need 
old time-step and present time-step values. 
Hence, in the local cell equation, the parameters
\texttt{scale} and \texttt{$scale_ico$}
are used to distinguish these terms:
\begin{lstlisting}
  void CellEquation(...)
   {
      local_cell_vector(i) +=  
          scale * (\nabla v^{n+1}, \nabla \phi) + etc.

      local_cell_vector(i) +=  
          scale_ico * (-p^{n+1},\nabla\cdot v)
   }
\end{lstlisting}
Analogous procedure is performed in the local 
cell matrix.

In addition to stationary problems, the implementation
of the time-derivative must be considered which is done
in 
\begin{lstlisting}
  void CellTimeEquation(...)
   {
     local_cell_vector(i) += 
         scale * (u^{n+1},\phi) + etc. 
   }
\end{lstlisting}
and it is done in a straight-forward way:
\begin{lstlisting}
  for (all quadrature points per cell q)
   {
     Tensor<1,2> u = ...;

     for (all dofs per cell i)
      {
        const Tensor<1,2> phi_i_u = ...;

        local_cell_vector(i) +=  
          scale * (u * phi_i_u) * 
          state_fe_values.JxW(q_point);
      }
   }
\end{lstlisting}
Here, the advantage is that \dope{} orders the terms in the time-stepping
problems
such that only $(u^{n+1},\phi)$ must be implemented.

>>>>

Finally, we note that to compute the requested functional value 
all that is left is to evaluate the functional in the computed solution 
which can be done again using an appropriate integrator method.
Since the sequence of events sketched above is again independent of the 
exact problem we introduce another container around it which we call 
\texttt{StatPDEProblem} that then simply provides the user with the 
method
\begin{lstlisting}
  template<class NEWTON>
      void StatPDEProblem<NEWTON>::ComputeReducedFunctionals();
\end{lstlisting}
The template argument \texttt{NEWTON} represents the choosen solver of the nonlinear problems.
That combines all the necessary steps to calculate $J(u_h)$.

@@

  LocalPDE local_pde;
  LocalFunctional local_functional;

@@

  SpaceTimeHandler dof_handler(triangulation, finite_element);

@@

  PDEProblemContainer<LocalPDE> prob_container(local_pde,
                                               dof_handler);

\end{lstlisting}
After that, we add the functional under consideration and, because it is a boundary functional, we specify the part of the boundary on which the functional operates (this is done via a 'boundary color', $1$ represents $\Gamma_{circ}$).
\begin{lstlisting}

@@

  typedef StatPDEProblem<NEWTONSOLVER> SSOLVER;

@@

  typedef NewtonSolver<LINEARSOLVER> NEWTONSOLVER;

\end{lstlisting}
The  template parameter \texttt{LINEARSOLVER} describes which linear solver we use in this example. We opted for a direct solver, so: 
\begin{lstlisting}

  typedef DirectLinearSolver<MATRIX, VECTOR> LINEARSOLVER;

@@

The pressure and incompressibility terms should be 
treated fully implicitly when time-discretizing 
the Navier-Stokes equations.
For this reason, the implementation is split up
into several items to account for fully implicit 
terms and remaining terms for which we need 
old time-step and present time-step values. 
Hence, in the local cell equation, the parameters
\texttt{scale} and \texttt{scale\_ico}
are used to distinguish these terms:
\begin{lstlisting}
  void CellEquation(...)
   {
   // Usual loops over DoFs and quadrature points
     {
      local_cell_vector(i) +=  
          scale *// terms like (\nabla v^{n+1}, \nabla \phi) etc.
          + scale_ico *// terms like (-p^{n+1},\nabla\cdot \phi)
     }
   }
\end{lstlisting}
Analogous procedure is performed in the local 
cell matrix.

In addition to stationary problems, the implementation
of the time-derivative must be considered which is done
in 
\begin{lstlisting}
  void CellTimeEquation(...)
   {
      //implement (u^{n+1},\phi)
   }
\end{lstlisting}
% \begin{lstlisting}
%   void CellTimeEquation(...)
%    {
%      local_cell_vector(i) += 
%          scale * (u^{n+1},\phi) + etc. 
%    }
% \end{lstlisting}
and it is done in a straight-forward way:\marginpar{Mir gefaellt dieses Auseinanderziehen nicht so wirklich...ist dieser zweite Abschnitt heir notwendig?}
\begin{lstlisting}
  for (/*all quadrature points per cell q*/)
   {
     Tensor<1,2> u = ...;

     for (/*all dofs per cell i*/)
      {
        Tensor<1,2> phi_i_u = ...;
        local_cell_vector(i) +=  scale * (u * phi_i_u) * 
                                  state_fe_values.JxW(q_point);    
      }
   }
\end{lstlisting}
Here, the advantage is that \dope{} orders the terms in the time-stepping
problems
such that only $(u^{n+1},\phi)$ must be implemented.
